Runtime Feedback in a Meta-Tracing JIT for Efficient Dynamic Languages

### 2011-03-28 talk/icooolps2011/paper.tex
improve conclusion

\section{Conclusion and Next Steps}

In this paper we presented two hints that can be used in the source code of an
interpreter written with PyPy. They are used to influence what the optimizer
does with the trace. We also showed how a small but still relevant dynamic
object model can use these hints to no longer use any dictionary lookups after
tracing. Instead a number of guards are inserted into the trace to check whether
the assumptions about the objects are still true. This makes operations on
objects seriously faster.

>>>>

\section{Conclusion}

In this paper we presented two hints that can be used in the source code of an
interpreter written with PyPy. They give control over runtime feedback and
optimization to the language implementor. They are expressive enough for
building well-known virtual machine optimization techniques, such as maps and
inline caches. We believe that they are flexible enough to express a wide
variety of language semantics efficiently.
